The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
work hab sel perspective

Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the "disproportionate use of
available" [@Mayor_2009] landscape resources or features by animals. Johnson
(1980) identified four orders of habitat selection: (1) the geographical range
of a species, (2) the home range of an individual, (3) the habitat patches
within the home range and (4) specific resources within a habitat patch.
Combined, habitat selection and social structure are intimately linked as
individuals must share space to interact [@Farine_2015] and resource
availability and quality influence home range size and overlap. Multilayer
networks represent a novel framework for considering the influence of habitat
selection and space use on sociality across scales.

>>>>

Social structure influenced by large scale processes, eg resources
Animals select for these same processes, habitat selection, as measured by RSF
All of these processes are influenced by scale: 
RSFs are are influenced
Habitat selection johnsons four orders Mayor 2009, scale can be explicitly considered
sociality across scales of sociality + temporal and spatial as shown above
ML networks present a framework for this

Social structure is influenced by large scale processes such as resource
availability and seasonality [@Peigner_2019], configuration [@He_2019] and
fragmentation [@Banks_2007]. Habitat selection is the "disproportionate use of
available" [@Mayor_2009] landscape resources or features by animals. Combined, habitat selection and social structure are intimately linked as
individuals must share space to interact [@Farine_2015] and resource
availability and quality influence home range size and overlap. Johnson
(1980) identified four orders of habitat selection: (1) the geographical range
of a species, (2) the home range of an individual, (3) the habitat patches
within the home range and (4) specific resources within a habitat patch.
 Multilayer
networks represent a novel framework for considering the influence of habitat
selection and space use on sociality across scales.
